### 2022-03-08 manuscript.tex
tuba4 [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/979aac6c91cdcd60c73bd3dfdcd768979d6a1696.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/979aac6c91cdcd60c73bd3dfdcd768979d6a1696/checks
https://github.com/scherzerthesis/thesis/actions/runs/1952757377

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/188382bd4c0e8176aaab45f4a32f8536d20901a0/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/188382bd4c0e8176aaab45f4a32f8536d20901a0}{scherzerthesis/thesis@188382b}
on March 8, 2022.

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/979aac6c91cdcd60c73bd3dfdcd768979d6a1696/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/979aac6c91cdcd60c73bd3dfdcd768979d6a1696}{scherzerthesis/thesis@979aac6}
on March 8, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}
